\section{Introduction}

Low-rank training methods reduce optimizer state and update rank by restricting
adaptation to a subspace. This introduces an immediate question: what should be
done with the discarded component of the gradient? The answer matters because
the projected branch may converge quickly while a stale or biased subspace still
misses a nontrivial orthogonal gradient. In that regime, progress depends on
how the discarded direction is recovered.

\Fira-style methods recover that discarded component by scaling it with
information extracted from the low-rank adaptive branch. This mechanism is
intuitively appealing and empirically useful, but it should not be confused
with Error Feedback. Classical Error Feedback stores the compression error in a
residual buffer and reintroduces that residual later. Norm recovery instead
uses the current projected adaptive state to rescale the current discarded
gradient. The recovery branch therefore inherits whatever mismatch exists
between projected adaptive statistics and the omitted coordinates.

This paper studies that boundary. We focus on stale-subspace diagnostics, where
the projected coordinate can vanish before the orthogonal coordinate does. In
that regime, the recovery scale itself may vanish and the cumulative recovered
mass may remain finite. The consequence is a nonzero orthogonal gradient even
though the full gradient is observable at each step.

Our contributions are deliberately narrow.
\begin{itemize}
\item We formalize why \Fira-style norm recovery is not Error Feedback and
separate discarded-gradient magnitude compensation from residual accumulation.
\item We prove a verified two-dimensional positive-$\epsilon$ stale-subspace
failure (Theorem~\ref{thm:positive-epsilon-failure}) and two repair results:
lower-bounded clipping (Theorem~\ref{thm:clipping-repair}) and separated
raw-gradient residual transmission with adaptive recovery scaling
(Theorem~\ref{thm:becr-repair}).
\item We state a contractive raw-gradient compressor
(Proposition~\ref{prop:becr-contractivity}) and a \BECR-SGD nonconvex
abstraction (Theorem~\ref{thm:becr-sgd}) without claiming Adam convergence or
compressed Adam-state compensation.
\item We integrate corrected synthetic diagnostics built under exact-Fira
labeling guards, moving-projection state audits, and CRN/provenance tracking.
\end{itemize}

The paper is therefore a theory/mechanism paper. It does not claim optimizer
superiority over AdamW or LDAdam, does not validate neural performance, and
does not infer broad behavior for all official \Fira code paths.
