\section{Bounded Recovery and \BECR}

Two repairs follow naturally from Theorem~\ref{thm:positive-epsilon-failure}.
The first keeps the recovery branch but lower-bounds its applied scale. The
second adds a residual state in raw-gradient units and separates raw
transmission from adaptive preconditioning.

\begin{theorem}[Lower-bounded clipping repairs the $2$D failure]
\label{thm:clipping-repair}
Under the same quadratic and stale projector as in
Theorem~\ref{thm:positive-epsilon-failure}, define
\[
s_t = \operatorname{clip}\!\left(\phi_t, s_{\min}, s_{\max}\right),
\qquad
0<s_{\min}\le s_{\max}<\frac{2}{\eta b},
\]
and update
\[
x_{t+1}=x_t-\eta \frac{a x_t}{|a x_t|+\epsilon_a},
\qquad
y_{t+1}=y_t-\eta s_t b y_t.
\]
If $0<\eta a<2\epsilon_a$, then
\[
x_t\to 0,\qquad y_t\to 0,\qquad \norm{\grad f(x_t,y_t)}\to 0.
\]
\end{theorem}

Clipping does not reconstruct adaptive moments for the orthogonal branch. It is
best understood as a diagnostic repair: once the applied recovery scale is kept
strictly positive, the orthogonal stale channel can no longer vanish by scale
collapse alone.

\begin{theorem}[Separated $\rho/s$ \BECR\ repairs the $2$D failure]
\label{thm:becr-repair}
Under the same $x$-update as in
Theorem~\ref{thm:positive-epsilon-failure}, define
\[
h_t = b y_t + e_t,\qquad
z_t = \rho h_t,\qquad
e_{t+1} = h_t - z_t,\qquad
y_{t+1} = y_t - \eta s_t z_t,
\]
with
\[
s_t = \operatorname{clip}\!\left(\phi(a x_t), s_{\min}, s_{\max}\right).
\]
Assume
\[
0 < \eta a < 2\epsilon_a,\qquad
s_{\min}>0,\qquad
0 < \rho < \frac{4}{2+\eta b s_{\min}}.
\]
Then
\[
x_t \to 0,\qquad (y_t,e_t)\to(0,0),\qquad \norm{\grad f(x_t,y_t)}\to 0.
\]
The $(y_t,e_t)$ subsystem is governed by
\[
A=
\begin{bmatrix}
1-\eta b \rho s_{\min} & -\eta \rho s_{\min} \\
b(1-\rho) & 1-\rho
\end{bmatrix},
\]
whose characteristic polynomial is
\[
\lambda^2 - \bigl(2-\rho(1+\eta b s_{\min})\bigr)\lambda + (1-\rho),
\]
and the Jury/Schur condition is precisely
\[
0 < \rho < \frac{4}{2+\eta b s_{\min}}.
\]
\end{theorem}

The separation is crucial. $h_t$, $z_t$, and $e_t$ live in raw-gradient units;
$s_t$ preconditions only the transmitted raw signal in the parameter update.
The residual update is therefore
\[
E_{t+1}=H_t-Z_t^{\mathrm{eff}},
\]
not $E_{t+1}=H_t-s_t Z_t$.

\begin{proposition}[\BECR\ projection compressor contractivity]
\label{prop:becr-contractivity}
Define the \BECR\ raw-gradient transmission operator
\[
\mathcal C_t^{\mathrm{BECR}}(v)=C_t(v)+\rho_t\bigl(v-C_t(v)\bigr),
\]
where $C_t(v)=P_tP_t^\top v$ is an orthogonal projector and
\[
\rho_t\in[\rho_{\min},\rho_{\max}] \subset (0,2).
\]
Define
\[
\delta=
1-\max\{|1-\rho_{\min}|,\;|1-\rho_{\max}|\}^2.
\]
Then
\[
v-\mathcal C_t^{\mathrm{BECR}}(v)=(1-\rho_t)(I-C_t)v
\]
and therefore
\[
\norm{v-\mathcal C_t^{\mathrm{BECR}}(v)}^2
\le (1-\delta)\norm{v}^2.
\]
In particular, $\mathcal C_t^{\mathrm{BECR}}$ is a $\delta$-contractive
raw-gradient transmission operator. When $\rho_t=1$, the operator reduces to
identity transmission $\,\mathcal C_t^{\mathrm{BECR}}(v)=v$, which is not
communication compression.
\end{proposition}
