\section{\BECR-SGD Abstraction}

The $2$D repair theorem isolates a raw-gradient residual mechanism. To state a
nonconvex convergence result without making Adam claims, we therefore move to a
constant-step SGD abstraction in which the projector/compressor is replaced by
a conditionally contractive \BECR\ transmission operator.

\begin{theorem}[\BECR-SGD nonconvex convergence]
\label{thm:becr-sgd}
Let $\{\mathcal F_t\}_{t\ge 0}$ be a filtration and let $f:\R^d\to\R$ be
$L$-smooth and lower bounded by $f_\star$. Suppose the stochastic gradients
$g_t$ satisfy
\[
\E[g_t\mid \mathcal F_t]=\grad f(x_t),\qquad
\E\!\left[\norm{g_t-\grad f(x_t)}^2\mid \mathcal F_t\right]\le \sigma^2.
\]
After drawing $g_t$, define the enlarged sigma-field
\[
\mathcal G_t=\sigma(\mathcal F_t,g_t).
\]
Assume any compressor randomness used by $C_t^{\mathrm{BECR}}$ is conditionally
independent after $\mathcal G_t$, and let $C_t^{\mathrm{BECR}}$ be
conditionally $\delta$-contractive in the sense that, for every
square-integrable $\mathcal G_t$-measurable vector $v_t$,
\[
\E\!\left[\norm{v_t-C_t^{\mathrm{BECR}}(v_t)}^2\mid \mathcal G_t\right]
\le (1-\delta)\norm{v_t}^2,
\qquad \delta\in(0,1).
\]
Assume $e_0=0$, let $\eta>0$ be constant, and define
\[
p_t=g_t+e_t,\qquad
q_t=C_t^{\mathrm{BECR}}(p_t),\qquad
e_{t+1}=p_t-q_t,\qquad
x_{t+1}=x_t-\eta q_t.
\]
Then $p_t=g_t+e_t$ is $\mathcal G_t$-measurable. Set
\[
K_\delta=\frac{2(1-\delta)(2-\delta)}{\delta^2},
\]
which is well-defined and strictly positive because $\delta\in(0,1)$. Assume
\[
\eta\le \frac{1}{2L},
\qquad
\eta\le \frac{1}{2L\sqrt{K_\delta}}.
\]
Then, for every $T\ge 1$,
\[
\frac{1}{T}\sum_{t=0}^{T-1}\E\!\left[\norm{\grad f(x_t)}^2\right]
\le
\frac{8(f(x_0)-f_\star)}{\eta T}
+
4L\eta\sigma^2
+
4L^2K_\delta \eta^2\sigma^2.
\]
In particular, choosing $\eta=\Theta(T^{-1/2})$ yields the standard
$O(T^{-1/2})$ rate for the average squared gradient norm.
\end{theorem}

The scope of Theorem~\ref{thm:becr-sgd} is intentionally narrow. It is a
constant-step SGD abstraction of raw-gradient residual transmission; it is not
an Adam convergence theorem, does not compensate compressed Adam optimizer
states, and does not subsume LDAdam-style generalized Error Feedback. The
identity case $\delta=1$ is excluded from the residual-energy proof only to
avoid the degenerate $K_\delta=0$ division. In that case,
$C_t^{\mathrm{BECR}}(v)=v$ almost surely, $e_t=0$ for all $t$ when $e_0=0$,
and the method reduces to standard SGD; the standard SGD bound applies. This
is also the case where \BECR\ transmits the dense complement exactly and is not
compression. For variable step sizes, the perturbed iterate satisfies
\[
\tilde x_{t+1}
=
\tilde x_t-\eta_t g_t+(\eta_t-\eta_{t+1})e_{t+1},
\]
so that an additional drift term appears. That regime is not covered here and
requires additional drift control.
