\section{Limitations}

This draft has several deliberate boundaries. First, we do not prove that
original \Fira generally fails, and we do not prove that exact \Fira generally
converges. The exact-Fira parity harness in this repository validates only a
read-only oracle on tested small fixtures. Second, Theorem~\ref{thm:becr-sgd}
is an SGD abstraction, not an Adam convergence theorem. Third, we do not
include neural diagnostics: CIFAR, MNIST, WikiText, and TinyGPT remain blocked
and are not used as evidence here.

Fourth, \BECR's cleanest theory uses a full raw-gradient residual $e_t$. This
residual is a mechanism for exact error conservation, not a free memory
optimization. We use residual accumulation for the EF mechanism and
error-feedback buffer for the persistent storage of $e_t$. For arbitrary dense
recovery errors, exact EF-style conservation requires enough persistent
information to reconstruct the residual, which is $O(d)$ in the worst case.
Thus full-residual \BECR\ preserves low-rank Adam states but may add a
parameter-size residual buffer unless it is implemented by reusing gradient
storage or by offloading/compressing the residual. Gradient-buffer reuse is a
systems optimization and must be validated by peak-memory measurements;
compressed or approximate residuals weaken exact EF guarantees and require
separate theory. Memory-limited residuals are approximate Error Feedback. If
the full residual is compressed, the conservation law becomes defective,
$q_t+\hat e_{t+1}=g_t+\hat e_t-c_{t+1}$. Appendix~\ref{app:compressed-residual-becr}
shows that \BECR-SGD then inherits the full-residual bound plus an explicit
residual-compression defect term; without martingale or alignment structure,
the leading defect contribution is $\mathcal C_T/T$, not
$\eta\mathcal C_T/T$. The memory accounting in this paper is synthetic and CPU only:
the artifact schema records residual bytes, projection bytes, and
optimizer-state bytes, but we do not validate GPU peak memory or claim
memory-neutrality. Fifth, LDAdam is treated as the closest related prior art,
but we do not offer an empirical LDAdam comparison in this draft. Finally, the
corrected synthetic evidence shows that clipping already repairs the
fixed-stale orthogonal channel; \BECR\ should therefore be read as a
residualized repair mechanism, not as a universal improvement over clipping.

\section{Conclusion}

The main message is narrow and testable: \Fira-style norm recovery is not Error
Feedback. In stale-subspace regimes, positive-$\epsilon$ recovery can send only
finite cumulative mass through the discarded branch and leave a nonzero
orthogonal gradient. Lower-bounded recovery and separated raw-gradient residual
transmission repair that failure in controlled diagnostics. The resulting
package supports a theory/mechanism paper centered on recovery-branch behavior,
while explicitly leaving neural validation, Adam convergence, and broader
optimizer comparisons for later work.
