The additional ablations retained from the corrected synthetic package are:
\begin{itemize}
\item no-lower-bound residual transmission (\texttt{rho\_no\_lower\_bound});
\item coupled residual transmission with $\rho_t=\phi_t$;
\item refresh-sweep state-reset, official-carry, projection-aware transport,
and full current-projection residual modes;
\item anisotropic CRN diagnostics and paired differences;
\item CPU-only memory/runtime accounting.
\end{itemize}

\subsection{Memory lower bound for exact residual conservation}

We use residual accumulation for the EF mechanism and error-feedback buffer for
the persistent storage of $e_t$.

\begin{proposition}[No-free-lunch note for exact dense Error Feedback]
\label{prop:memory-lower-bound}
For arbitrary dense residuals, any exact implementation of the EF identity
\[
q_t + e_{t+1} = g_t + e_t
\]
that works for all future inputs must store sufficient information to
reconstruct $e_t$. Under finite-precision storage or continuous
finite-dimensional state models, this requires $\Omega(d)$ persistent
information in the worst case.
\end{proposition}

\begin{proof}[Proof sketch.]
Exact EF requires forming the next compensated gradient
\[
p_{t+1}=g_{t+1}+e_{t+1}.
\]
Suppose two distinct residuals $e\neq e'$ map to the same persistent internal
state $s$. At the next step choose the same future gradient $g_{t+1}$ for both
histories. Exact EF then requires different compensated signals
$g_{t+1}+e$ and $g_{t+1}+e'$, but the algorithm cannot distinguish the two
histories from the same state $s$. This contradiction shows that the
persistent state must uniquely encode every possible residual in the residual
set. Under finite-precision storage, encoding an arbitrary dense $d$-vector to
fixed accuracy requires $\Omega(d)$ words in the worst case. Under continuous
finite-dimensional state with continuous update and readout maps,
invariance-of-domain style reasoning rules out an injective continuous
encoding of an open subset of $\mathbb{R}^d$ into $\mathbb{R}^m$ for $m<d$.
Hence exact dense residual conservation has an $\Omega(d)$
persistent-information requirement in the worst case.
\end{proof}

\paragraph{Scope.}
This is a no-free-lunch observation, not a headline theorem. It depends on a
reasonable finite-precision or continuous-state storage model. It does not
rule out gradient-buffer aliasing, CPU offload, low precision, sparse or
low-rank residuals under additional structure, or approximate residual
compression. It only rules out exact dense residual conservation with
sublinear persistent information in the worst case. Compressed residual
variants are approximate EF and require separate theory.

\subsection{Memory-limited BECR as approximate Error Feedback}
\label{app:compressed-residual-becr}

We now consider a memory-limited \BECR\ variant in which the persistent
error-feedback buffer is replaced by an approximate residual $\hat e_t$. The
update is
\[
\hat p_t = g_t + \hat e_t,\qquad
q_t = C_t^{\mathrm{BECR}}(\hat p_t),\qquad
r_t = \hat p_t - q_t,\qquad
\hat e_{t+1} = S_t(r_t),\qquad
x_{t+1} = x_t - \eta q_t.
\]
Define the residual-compression defect
\[
c_{t+1} = r_t - \hat e_{t+1} = r_t - S_t(r_t).
\]
Then the conservation law becomes defective:
\[
q_t + \hat e_{t+1}
=
g_t + \hat e_t - c_{t+1}.
\]
All of $\hat e_t$, $\hat p_t$, $q_t$, $r_t$, and $c_{t+1}$ are raw-gradient
units, and the learning rate appears only in the parameter update. This is
approximate Error Feedback, not exact EF; once $c_{t+1}\neq 0$, the method is
no longer exact EF.

\paragraph{Assumptions.}
Let $f:\mathbb R^d\to\mathbb R$ be $L$-smooth and lower bounded by $f_\star$.
Let $\{\mathcal F_t\}_{t\ge 0}$ be the filtration before sampling $g_t$, and
assume
\[
\E[g_t\mid \mathcal F_t]=\grad f(x_t),\qquad
\E\!\left[\norm{g_t-\grad f(x_t)}^2\mid \mathcal F_t\right]\le \sigma^2.
\]
After drawing $g_t$, define
\[
\mathcal G_t = \sigma(\mathcal F_t,g_t).
\]
Assume $C_t^{\mathrm{BECR}}$ is conditionally $\delta$-contractive on
post-gradient signals:
\[
\E\!\left[\norm{v_t-C_t^{\mathrm{BECR}}(v_t)}^2\mid \mathcal G_t\right]
\le (1-\delta)\norm{v_t}^2
\]
for every square-integrable $\mathcal G_t$-measurable $v_t$, with
$\delta\in(0,1)$ for the residual-energy proof. Let $\eta>0$ be constant,
$\hat e_0=0$, and define the cumulative defect budget
\[
\mathcal C_T := \sum_{t=0}^{T-1}\E\norm{c_{t+1}}^2.
\]
All constants below are conservative and are stated only to keep the defect
accounting explicit.

\begin{proposition}[Approximate residual-energy lemma]
\label{prop:approx-becr-residual-energy}
Define
\[
K_{\delta}^{\mathrm{AR}} := \frac{2(2-\delta)(4-\delta)}{\delta^2},
\qquad
J_{\delta}^{\mathrm{AR}} := \frac{4(2-\delta)}{\delta^2}.
\]
Then, for every $T\ge 1$,
\[
\sum_{t=0}^{T-1}\E\norm{\hat e_t}^2
\le
K_{\delta}^{\mathrm{AR}}
\left(
\sum_{t=0}^{T-1}\E\norm{\grad f(x_t)}^2
+
T\sigma^2
\right)
+
J_{\delta}^{\mathrm{AR}}\mathcal C_T.
\]
\end{proposition}

\begin{proof}[Proof sketch.]
Write $r_t=\hat p_t-q_t=\hat e_{t+1}+c_{t+1}$ and condition on
$\mathcal G_t$. The exact-EF residual-energy proof controls the
post-compression residual through the contractive complement
$\hat p_t-C_t^{\mathrm{BECR}}(\hat p_t)$; the only change is that
$\hat e_{t+1}$ now differs from that complement by the residual-compression
defect $c_{t+1}$. Expanding
$\norm{\hat p_t}^2\le 2\norm{g_t}^2 + 2\norm{\hat e_t}^2$, using conditional
variance, and applying Young's inequality to the added defect terms yields the
stated bound. The $J_{\delta}^{\mathrm{AR}}\mathcal C_T$ term is exactly what
distinguishes approximate EF from exact EF.
\end{proof}

\paragraph{Perturbed iterate identity.}
Define
\[
\tilde x_t = x_t - \eta \hat e_t.
\]
Using the defective conservation law,
\[
\tilde x_{t+1}
=
x_t-\eta q_t-\eta \hat e_{t+1}
=
\tilde x_t-\eta g_t+\eta c_{t+1}.
\]
This identity is mandatory: compressed residual BECR behaves like approximate
EF with an additive raw-gradient defect sequence.

\begin{theorem}[General defect-budget theorem]
\label{thm:compressed-becr-general-defect}
Assume
\[
\eta\le \frac{1}{8L},
\qquad
L^2\eta^2 K_{\delta}^{\mathrm{AR}}\le \frac{1}{8}.
\]
Then, for every $T\ge 1$,
\[
\frac{1}{T}\sum_{t=0}^{T-1}\E\norm{\grad f(x_t)}^2
\le
\frac{8(f(x_0)-f_\star)}{\eta T}
+
8L\eta\sigma^2
+
8L^2\eta^2 K_{\delta}^{\mathrm{AR}}\sigma^2
+
\left(20 + 8L\eta + 8L^2\eta^2J_{\delta}^{\mathrm{AR}}\right)\frac{\mathcal C_T}{T}.
\]
Without martingale or alignment assumptions on $c_{t+1}$, the leading defect
contribution is therefore $\mathcal C_T/T$, not $\eta\mathcal C_T/T$. If
$\mathcal C_T/T=O(1)$, the bound allows a constant defect floor. To retain
$O(T^{-1/2})$ stationarity with $\eta=\Theta(T^{-1/2})$, one needs
$\mathcal C_T/T = O(T^{-1/2})$ or stronger.
\end{theorem}

\begin{proof}[Proof sketch.]
Apply smoothness to $f(\tilde x_t)$ under
$\tilde x_{t+1}=\tilde x_t-\eta g_t+\eta c_{t+1}$. Without extra structure on
$c_{t+1}$, the cross term
$\langle \grad f(\tilde x_t), c_{t+1}\rangle$ has no cancellation and must be
bounded by Young's inequality, which yields a first-order defect contribution
of order $\mathcal C_T/T$ rather than $\eta\mathcal C_T/T$. The transfer from
$\grad f(\tilde x_t)$ to $\grad f(x_t)$ introduces the residual-energy bound
from Proposition~\ref{prop:approx-becr-residual-energy}. The constants above
are conservative and are not intended as a sharp estimate.
\end{proof}

\begin{theorem}[Aligned or martingale defect theorem]
\label{thm:compressed-becr-aligned-defect}
Assume the hypotheses of
Theorem~\ref{thm:compressed-becr-general-defect}. Suppose in addition that the
defect sequence satisfies an alignment or cancellation condition:
\[
\sum_{t=0}^{T-1}\E\inner{\grad f(\tilde x_t)}{c_{t+1}}
\le
\alpha \sum_{t=0}^{T-1}\E\norm{\grad f(x_t)}^2
+
\chi \eta \mathcal C_T
\]
for some $\alpha\in[0,1/8)$ and $\chi\ge 0$. A conditional mean-zero
martingale defect with enough independence is a special case with $\alpha=0$.
Then
\[
\frac{1}{T}\sum_{t=0}^{T-1}\E\norm{\grad f(x_t)}^2
\le
\frac{8(f(x_0)-f_\star)}{\eta T}
+
O(L\eta\sigma^2)
+
O(L^2\eta^2K_{\delta}^{\mathrm{AR}}\sigma^2)
+
O\!\left((1+\chi)\eta \frac{\mathcal C_T}{T}\right),
\]
where the hidden constants depend only on $\alpha$, $L$, and $\delta$. Under
this stronger structure, $\eta=\Theta(T^{-1/2})$ remains compatible with the
usual $O(T^{-1/2})$ stationarity rate when $\mathcal C_T/T=O(1)$.
\end{theorem}

\begin{proof}[Proof sketch.]
The additional assumption lets the first-order defect term scale like
$\eta\mathcal C_T/T$ instead of $\mathcal C_T/T$. This is a strong
assumption: it is not implied by residual compression alone, and it must come
from alignment, martingale cancellation, or another explicit structural model
for the defect sequence.
\end{proof}

\paragraph{Identity-transmission case \texorpdfstring{$\delta=1$}{delta=1}.}
If $C_t^{\mathrm{BECR}}(v)=v$ almost surely on the relevant signal, then
$r_t=0$. If $S_t(0)=0$ and $\hat e_0=0$, then $\hat e_t=0$ and
$c_{t+1}=0$ for all $t$, so the method reduces to standard SGD. The
residual-energy constants above are not used in this degenerate identity case.

\paragraph{Corollaries and examples.}
\begin{itemize}
\item \textbf{Low-rank residual basis.}
If $\hat e_{t+1}=B_tB_t^\top r_t$, then
$c_{t+1}=(I-B_tB_t^\top)r_t$. Whenever
$\sum_{t<T}\E\norm{c_{t+1}}^2\le \mathcal C_T$, the general theorem applies.
This is an approximate-EF accounting only; it is not a novelty claim over
GreedyLore or related low-rank compressors.
\item \textbf{Sketched, sparse, or top-$k$ residuals.}
The same defect budget applies through $\mathcal C_T$, and unbiased variants
can instead be analyzed through a martingale variance budget if the
mean-zero condition is justified.
\item \textbf{Biased residual estimators.}
A persistent bias in $c_{t+1}$ yields a stationarity neighborhood unless the
bias energy is sublinear or is explicitly aligned.
\item \textbf{Contractive residual compressors.}
Even if $S_t$ is contractive on $r_t$, extra assumptions are still needed to
bound $\mathcal C_T$ because $r_t$ itself depends on the evolving approximate
buffer $\hat e_t$. One-level contractivity of $S_t$ does not preserve exact
EF by itself.
\end{itemize}

\paragraph{Novelty boundary.}
MicroAdam compresses correction information for adaptive optimization;
LDAdam uses generalized EF for low-dimensional Adam gradient and optimizer-state
compression; GreedyLore studies low-rank gradient compression with EF and
convergence; and classical compressed EF already covers many generic
compressed-residual ideas \citep{microadam,ldadam,greedylore,errorfeedback}.
Our note is only an approximate-EF accounting for \Fira-style recovery-branch
residuals. It is not a new compressed-EF framework and not Adam-state
compensation.

\paragraph{Memory implication.}
Full residual BECR stores a full-size error-feedback buffer and therefore keeps
exact EF at $O(d)$ resident information. A compressed residual may reduce
resident memory to $O(k)$ or another compressed budget, but only by accepting
residual-compression defect and therefore approximate EF rather than exact EF.
Peak GPU memory savings still require measurement, and no memory-neutrality
claim follows from this appendix note.

\paragraph{Limitations.}
This section adds theory only. It does not implement compressed residuals, does
not validate any compressor experimentally, and does not prove Adam
convergence. The deterministic theorem gives a $\mathcal C_T/T$ defect floor.
The more favorable $\eta\mathcal C_T/T$ scaling requires explicit alignment or
martingale cancellation and should not be assumed for arbitrary compressors.

\begin{table}[h]
\caption{Claim--evidence matrix for the integrated draft.}
\label{tab:claim-evidence}
\input{tables/claim_evidence_matrix}
\end{table}

\begin{table}[h]
\caption{Synthetic CPU memory/runtime accounting.}
\label{tab:memory-accounting}
\input{tables/memory_runtime_accounting}
\end{table}

The memory table should not be read as a GPU memory claim. It records whether
the corrected synthetic schema tracks residual bytes and related fields, and it
explicitly notes that no GPU peak-memory validation is part of this paper.
